Wettability of Doped Two-Dimensional Materials

### 2017-02-22 writing/paper-Tian-gr-wetting.tex
Change abstract

% Created 2017-02-22 Wed 13:07
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\date{}
\title{Wettability of Doped Two-Dimensional Materials}
\begin{document}

\newpage{}
\begin{abstract}
  The emergence of 2D-material-based liquid-phase devices calls for
  the need for understanding the wetting property at the
  2D-material-liquid interface, and particularly the doping-induced
  tuning of wetting properties. In this letter, we propose a
  multiscale view of the doping-induced tunable wettability of 2D
  materials, by combining the reorientation effect of water molecules
  estimated by MD simulation, and the electrowetting effect calculated
  by continuum model. We reveal the electrostatic nature of the
  doping-induced wettability under both scale. We further evaluate the
  recent finding of doping-induced wettability tuning of graphene with
  the proposed model, by considering incomplete surface coverage of 2D
  materials. We find that minor surface incompleteness can cause great
  discrepancy in the measured value of interfacial wettability, requiring
  extreme care for interpreting the experimental results. In
  addition, we prove that a 2D material with higher density of states
  can essentially reduce the gating voltage in a 2D-material-based
  electrowetting device, and rank the tunability of the 2D materials
  as: MoTe$_{2}$ > MoS$_{2}$ > WTe$_{2}$ > WS$_{2}$ > germanene > silicene >
  graphene. Our multiscale analysis provides a comprehensive view of
  the wettability of 2D material interface, and we believe operational
  2D-material-based liquid manipulating devices will be facilitate by
  the principles presented in this letter.
\end{abstract}
\maketitle

>>>>

% Created 2017-02-22 Wed 14:18
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\date{}
\title{Wettability of Doped Two-Dimensional Materials}
\begin{document}

\newpage{}
\begin{abstract}
  Understanding molecular interactions between liquid and the doped two-dimensional (2D) 
  materials enables new technology opportunities in functional surfaces and ultrathin membranes. 
  Here, we develop the first theoretical framework to model the wettability of the doped two-dimensional 
  (2D) materials as a function of their doping level. Multiscale physical phenomena are considered, 
  including: (i) the change of 2D materials surface energy, 
  (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
  and (iii) the electrical double layer (EDL) formed in the liquid phase. 
  \textcolor{cyan}{We propose that the EDL effect dominates the contact angle change }
  and show that upon doping, the decrease of the equilibrium water contact angle on a sheet of defect-free, 
  monolayer 2D material is typically less than 7 degrees. 
  We then study the role of the surface defects and the influence of 2D material choice.
  \textcolor{cyan}{Our analysis show that the defect density has a great impact on the water contact angle on the doped
  2D materials, and is responsible for the discrepancy between the recent experimental observations and our proposed 
  theory. Based on the quantum capacitances (QCs) of various 2D materials calculated by density functional theory (DFT),
  we predict that when the the 2D materials is doped by electrostatic gating, 
  the contact angle change on 2D semiconductors (e.g. transition metal dichalcogenides (TMDCs)) is more
  sensitive to the gate voltage compared to that on 2D semimetals (e.g. graphene). 
  Selecting a 2D material with a higher QC essentially reduces the gate voltage required to reach the same doping level,
  and ensures a wider operational region in 2D-material-based liquid phase devices.}
  \textcolor{magenta}{
  FINAL CONCLUSIONS PLACE HOLDER.
  }

\end{abstract}
\maketitle
